\documentclass[a4paper]{article}

\usepackage{appendix}
\usepackage{cleveref}
\usepackage{enumitem}
\usepackage[margin=2.5cm]{geometry}
\usepackage[utf8]{inputenc}

\newenvironment{enumsection}[1]{\section{#1} \begin{enumerate}[ref=\thesection.\theenumi]}{\end{enumerate}}

\begin{document}

\title{The Constitution of the UWA AI Club}
\author{}
\date{}

\maketitle


\begin{enumsection}{Name}
    \item The formal name of the Club shall be \textbf{UWA Artificial Intelligence Club}.
    \item The Club may also be known as \textbf{UWA AI Club}.
    \item The Club shall henceforth be referred to as \textbf{UWA AI Club} and \textbf{AI Club}.
\end{enumsection}


\begin{enumsection}{Definitions}
    \item the University --- the University of Western Australia.
    \item the Guild --- the UWA Student Guild.
    \item the Club --- the UWA AI Club.
    \item Regulation --- a rule, passed by Committee, with ongoing consequences to the Club.
    \item Fresher --- a first time member of the club.
\end{enumsection}


\begin{enumsection}{Objectives} \label{sec:objectives}
    \item To provide an inclusive community for students interested in AI at UWA to connect, learn about, develop and use artificial intelligence.
    \item Provide AI specific services and events for students.
    \item To encourage and facilitate sharing of AI knowledge and skills at the University and within the wider community.
    \item To become and remain affiliated with the Societies Council of the Guild.
    \item To encourage and facilitate computer science and mathematics education at the University and within the wider community.
    \item To encourage and facilitate the holding of events and functions beneficial to Objectives of the Club.
    \item To encourage and promote cooperation between the Club and other societies and community-based organizations representative of the Club's interests.
    \item To ensure that the Club shall not by way of gift transmit any monies, grants or property to any person except in the direct cause of these Objectives and as detailed in \cref{sec:dissolution}.
\end{enumsection}


\begin{enumsection}{Membership of the Club}
    \item Club membership is targeted at, but not restricted to:
    \begin{enumerate}
        \item Students of the University
        \item Members of the Guild
        \item Past members of the Club
    \end{enumerate}
    \item Membership shall not be made available to persons who have been expelled (see \cref{sec:expulsion}).
    \item Honorary life membership may be conferred by a two-thirds majority of a General Meeting upon any member who has performed outstanding service to the Club.
    \item The annual subscription for members shall be set by the Committee of the Club, subject to any restrictions set by the Guild.
    \item A financial member is a member who has paid their annual subscription for this year.
    \item Financial memberships expire 1 day prior to the holding of the Annual General Meeting in the subsequent year from its payment (see \cref{sec:AGMs}).
\end{enumsection}


\begin{enumsection}{The Committee} \label{sec:committee}
    \item The Committee of the Club shall consist of:
    \begin{enumerate}
        \item The executive office bearers:
        \begin{itemize}
          \item President
          \item Vice-President
          \item Treasurer
          \item Secretary 
        \end{itemize}
        \item The non-executive Committee members:
        \begin{itemize}
            \item Fresher Representative
            \item Four Ordinary Committee Members
        \end{itemize}
        \item The Immediate Past President (optional, nonvoting, see \cref{sub:ipp_appointment})
    \end{enumerate}
    \item The Committee members shall remain in office until the next Annual General Meeting or until they lose the confidence of a General Meeting, at which their position is declared vacant (see \cref{sub:removing_committee}).
    \item \label{sub:removing_committee} By two-thirds majority vote, the General Meeting may remove any member of the Committee from office. They must then elect a member to that role, following the rules laid out in \cref{sec:AGMs}.
    \item If a Committee member ceases to meet the eligibility requirements for their position, as detailed in \cref{sec:AGMs}, they shall cease to hold office and the position shall be declared vacant.
    \item \label{sub:committee_resign} If a Committee member resigns or ceases to hold office for any reason, the vacancy shall either:
    \begin{enumerate}
        \item Be filled through appointment by Committee from the financial membership of the club, subject to review at the next General Meeting.
        \begin{enumerate}
            \item When reviewing, a simple majority vote of the General Meeting will confirm the appointment. If such a vote fails then the position must be immediately filled by election (as per \cref{sec:AGMs}).
        \end{enumerate}
        \item Remain vacant and be filled by election (as per \cref{sec:AGMs}) at the next General Meeting, which must be held within the next 2 weeks.
    \end{enumerate}
    \item No member of Committee may fill two roles simultaneously. Upon being appointed to a second position, they immediately cease to hold the first and are subject to the rules given in \cref{sub:committee_resign}.
    \item \label{sub:ipp_appointment} The Immediate Past President may, by executive decision of the new President, be granted a nonvoting advisory position on the Committee for the duration of the President's term.
\end{enumsection}


\begin{enumsection}{General Meetings} \label{sec:general_meetings}
    \item A General Meeting shall be open to all members of the Club.
    \item The quorum of a General Meeting shall consist of 12 financial members of the Club.
    \item The Committee may, at any time, call a Ordinary General Meeting of the Club.
    \item The Secretary shall call a Special General Meeting upon receiving a written requisition from at least 8 financial members of the Club.
    \begin{enumerate}
        \item The meeting shall be held no later than 14 days immediately following receipt of such requisition. 
        \begin{enumerate}
            \item If the secretary fails to call the meeting within that time, any of the signatories of the requisition may do so.
        \end{enumerate}
        \item \label{sub:special_meeting_priority} Any business set out in the requisition shall have priority over all other business. 
    \end{enumerate}
    \item The Secretary shall make all reasonable attempts (including but not limited to publications required by the Guild, and any official club publications) to notify all members of any General Meeting together with that meeting's agenda at least four days prior to the date appointed for that meeting.
    \begin{enumerate}
        \item This agenda may be changed during the meeting, subject to the restriction in \cref{sub:special_meeting_priority} if appropriate.
    \end{enumerate}
    \item No General Meeting may be held while a Guild General Meeting is in progress, except where the written notice of the meeting was given before the written notice of the Guild General Meeting. Any such meeting being conducted in contravention of this requirement shall disband immediately on the order of a disciplinary officer of the Guild.
    \item All General Meetings of the Club shall be conducted in accordance with the procedures in the Standing Rules and Orders of the Guild Council.
    \item The General Meeting shall, in addition to the powers expressly granted to it by this Constitution, have all powers which are granted to the Committee.
\end{enumsection}


\begin{enumsection}{Annual General Meetings of the Club} \label{sec:AGMs}
    \item The Club shall hold its Annual General Meeting within the first four weeks of each academic year.
    \item The Club may, at the Annual General Meeting, select a patron who, willing to do so, shall hold office until the succeeding Annual General Meeting.
    \item Before the Annual General Meeting, the Secretary shall call for nominations for the offices and Committee of the Club, and shall include the same in the notice of the Annual General Meeting. Nominations shall close at that meeting.
    \item The election of the Committee of the Club shall be conducted by approval voting (i.e. each member may vote for any number of candidates) subject to the following conditions:
    \begin{enumerate}
        \item Only financial members of the Club may nominate, vote, or be nominated.
        \item Absentee votes are only accepted in the form of explicit written instructions detailing the candidates and the positions the member is voting for those candidates to take.
        \item Members must have been members for at least 42 days prior to the election in order to be eligible to absentee vote.
        \item Absentee votes do not count towards quorum.
        \item All executive office bearers must be students at the University and Guild members for the duration of their term.
        \item \label{fresher_rep_requirement} Only Freshers shall be eligible for the position of Fresher Representative.
    \end{enumerate}
\end{enumsection}


\begin{enumsection}{Committee Meetings}
    \item The Committee shall meet as such times and places as the President, in consultation with the other Committee members shall determine.
    \item The quorum of a Committee meeting shall be 5 Committee members of which at least 3 must be executive office bearers. Nonvoting Committee positions do not count towards quorum.
    \item The Committee shall only exercise its powers (as defined in this constitution or in Regulations) at a properly convened meeting of the Committee, except as elsewhere provided in the Constitution.
    \item The Secretary or President shall cause all members of the Committee to receive three days notice of any such meeting including an agenda of the business to be discussed. This agenda may be expanded upon during the meeting.
    \begin{enumerate}
        \item A meeting may be called without this notice if 6 Committee members of which at least 3 are executive office bearers are present.
    \end{enumerate}
    \item The Secretary shall forthwith call a Special Committee Meeting upon receiving a written requisition from at least two Committee members.
    \begin{enumerate}
        \item Any such Special Meeting shall be held not later than seven days immediately following the receipt of such requisition.
        \begin{enumerate}
            \item If the Secretary fails to call the meeting within that time, any one of the members signing the requisition may do so. 
        \end{enumerate}
        \item Any business set out in the requisition shall have priority over all other business.
    \end{enumerate}
    \item All meetings of the Committee shall be conducted in accordance with the procedures prescribed in the Standing Rules and Orders of the Guild Council.
    \item Subject to this Constitution, the Committee shall be responsible for giving effect to the objectives of the Club (see \cref{sec:objectives}) and for carrying on its everyday business.
    \item Towards this end, the Committee shall have the power to:
    \begin{enumerate}
        \item Acquire and dispose of property, dispose of money, open banking accounts, and enter into contracts.
        \begin{enumerate}
            \item The Committee shall not borrow money or incur debts or liabilities on behalf of or in the name of the Club to an amount greater than five dollars per existing financial member of the Club.
        \end{enumerate}
        \item Make Regulations for the orderly and proper management of the affairs of the Club.
        \begin{enumerate}
            \item So long as no Regulation is in conflict with this Constitution.
        \end{enumerate}
        \item Impose fines for the breach of this Constitution or Regulations.
    \end{enumerate}
    \item These powers are in addition to any other powers given in this Constitution (in particular, see \cref{sec:member_suspension}).
\end{enumsection}


\begin{enumsection}{Duties and Powers} \label{sec:duties}
    \item The President shall have the following duties and powers, in addition to those elsewhere in the Constitution and in any Regulations: \label{sub:pres_duties}
    \begin{enumerate}
        \item To coordinate and supervise the work of the Committee.
        \item To carry out the will of the Club.
        \item To chair Committee and General Meetings of the Club.
        \item When immediate action is required in any matter affecting the interests of the Club \label{sub:exec_power}
        \begin{enumerate}
            \item To take such actions upon seeking the advice and agreement of another member of the Committee (preferably the Vice-President).
            \item Any actions taken as such, shall be subject to review at the next Committee meeting. 
        \end{enumerate}
    \end{enumerate}
    
    \item The Vice-President shall have the following duties and powers, in addition to those elsewhere in the Constitution and in any Regulations:
    \begin{enumerate}
        \item Assisting the President wherever possible. 
        \item Whenever the President is unavailable, to take on the duties and powers of the President as detailed in \cref{sub:pres_duties}.
    \end{enumerate}
    
    \item The Treasurer shall have the following duties, in addition to those elsewhere in the Constitution and in any Regulations:
    \begin{enumerate}
        \item To keep proper books of account dealing with the property and finances of the Club and to furnish the Committee with such information upon request.
        \item To arrange and be responsible for the handling of the petty cash.
        \item To prepare a financial statement detailing income and expenses during their term of office, for presentation at the Annual General Meeting.
        \item To produce and deliver all necessary books, vouchers and other documents to the persons appointed by the Guild for the purpose of conducting and audit, insofar as such persons require.
        \item To produce and deliver all necessary books, receipts and other documents to the persons appointed by the Guild for the purpose of obtaining grants, insofar as such persons require.
    \end{enumerate}
    
    \item The Secretary shall have the following duties, in addition to those elsewhere in the constitution and in any Regulations:
    \begin{enumerate}
        \item To record and distribute all proceedings of the Club in all meetings.
        \item To provide the Guild with information about the Club, upon request.
        \item To keep record of all Club members, and their contact information.
        \item To keep record of any members granted special powers, rights, or responsibilities by Committee.
        \item To keep record of any Regulations passed by Committee.
    \end{enumerate}
    
    \item The Fresher Representative shall have the following duties, in addition to those elsewhere in the constitution and in any Regulations:
    \begin{enumerate}
        \item To look out for the needs and rights of the Freshers.
        \item To be aware of, and acquainted with all Freshers of the Club, insofar as is possible.
        \item To be involved, insofar as is possible, in any Fresher targeted activity the Club may run.
    \end{enumerate}
    
    \item Should any of the Committee members be temporarily unable to fulfill their duties, as defined above, another willing member of Committee shall, at the request of Committee take on some or all of their duties.
\end{enumsection}


\begin{enumsection}{Finances} \label{sec:finances}
    \item All monies due and payable to the Club shall be received by the Treasurer who shall lodge them without undue delay in the Club Banking Account for the credit of the Club.
    \item Any two Committee members shall be empowered to jointly sign or otherwise approve forms of authority for the withdrawal of any money from the the Club's Banking Account.
    \item With exception of the executive power of the President (\cref{sub:exec_power}), no payments shall be made on behalf or in the name of the Club unless it has been authorised by the Committee.
\end{enumsection}

\begin{enumsection}{Major Obligations to the Guild} \label{sec:guild_obligations}
    \item The Club shall comply with the rules of the Guild and the Societies Council of the Guild, and all other provisions enrolled upon the Guild Statutes Book.
    \begin{enumerate}
        \item The executive office bearers shall jointly and severally responsible for such compliance.
    \end{enumerate}
    \item Such rules supersede the Regulations of the Club, and this Constitution, if and where contradiction occurs.
\end{enumsection}

\begin{enumsection}{Suspension of Members} \label{sec:member_suspension}
    \item The Committee has the ability to suspend any member if they believe it in the best interests of the Club. Such suspensions shall be reviewed at the next General Meeting of the Club.
    \item While suspended the member shall be unable to exercise any right as a member and shall not be permitted to take part in any activities or events run by the Club.
    \item The Committee, or General Meeting, may discontinue suspension and restore a member to normal standing, or impose other sanctions such as expulsion (see \cref{sec:expulsion}) or continued suspension for a fixed amount of time.
    \item \label{committee_suspended} If for any reason a Committee member is suspended, a General Meeting must be held within two weeks to resolve the situation.
\end{enumsection}


\begin{enumsection}{Expulsion of Members\label{sec:expulsion}}
    \item The General Meeting may, by two-thirds majority vote, expel any member of the Club.
    \item While expelled the former member shall be unable to exercise any right as a member. 
    \item Expulsion can be repealed by a two-thirds majority vote of a General Meeting.
    \item An expelled member remains expelled indefinitely and is barred from future membership.
\end{enumsection}


\begin{enumsection}{Availability of Constitution}
    \item This Constitution shall be made available to members on request.
\end{enumsection}


\begin{enumsection}{Alteration of Constitution}
    \item To amend this Constitution, the following steps must be taken:
    \begin{enumerate}
        \item Any two financial members of the Club may not less than four days before the day appointed for the next General Meeting submit to the Secretary a notice of motion by them proposing an alteration to the Constitution.
        \item The motion may then be considered at the next General Meeting of the Club.
        \item Further amendments which are relevant to the subject matter of the motion may be moved without notice.
        \item The motion or any amendment thereto shall be deemed adopted if it receives a two-thirds majority of the General Meeting.
        \item The motion as adopted, with any amendments, shall come into force upon receiving the approval of the Societies Council of the Guild.
    \end{enumerate}
    \item A history of revisions of this Constitution shall be maintained in \cref{app:history}. Where possible the Committee shall maintain details of these revisions and make these available to members upon request.
\end{enumsection}


\begin{enumsection}{Dissolution} \label{sec:dissolution}
    \item In the event of the Club's disaffiliation from the Societies Council of the Guild and cessation of activity, the resources of the Club shall be given into the holding of the University Computer Club.
    \begin{enumerate}
        \item These resources are given with the understanding that they shall be at the first opportunity passed on to another society or club affiliated with the Societies Council of the Guild and having similar objectives to those of the Club (see \cref{sec:objectives}), as judged by the University Computer Club.
    \end{enumerate}
    \item In the event that the University Computer Club no longer exists at the time of the Club's dissolution, the resources of the Club shall be given into the holding of the Societies Council of the Guild.
    \begin{enumerate}
        \item These resources are given with the understanding that they shall be at the first opportunity passed on to another society or club affiliated with the Societies Council of the Guild and having similar objectives to those of the Club (see \cref{sec:objectives}), as judged by the Societies Council of the Guild.
    \end{enumerate}
\end{enumsection}

\appendixpage

\appendix \section{History of this Constitution} \label{app:history}

\noindent Prepared by Jason Tadi \& John Clema. Drawing upon the Programming Competition Society constitution.

\medskip{}

\begin{itemize}
    \item[] Adopted by General Meeting on:  
\end{itemize}

\medskip{}

\noindent As witnessed by:
\begin{description}
\item [{Interim President:}] Jason Tadi\hrulefill
\item [{Interim Vice-President:}] Tyler Etherton\hrulefill
\item [{Interim Treasurer:}] John Clima\hrulefill
\item [{Interim Secretary:}] Ruan van Zyl\hrulefill
\end{description}

\end{document}
