\documentclass[12pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{helvet}  
\renewcommand{\familydefault}{\sfdefault}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[none]{hyphenat}
\titleformat{\section}{\large\bfseries}{}{0em}{}
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

\newenvironment{enumsection}[1]{\section{#1} \begin{enumerate}[ref=\thesection.\theenumi]}{\end{enumerate}}

\title{[INSERT CLUB NAME] Constitution}
\date{Current as at [insert date]}
\begin{document}
\maketitle

\tableofcontents

\section{1. Name}
\begin{enumerate}[label=1.\arabic*]
 \item The formal name of the Club shall be “[insert club name]”.
 \item The Club may also be known as “[insert club acronym]”.
 \item The Club shall henceforth be referred to as “[insert club name]” or “the Club”.
\end{enumerate}

\section{2. Preliminary}
\begin{enumerate}[label=2.\arabic*]
 \item “[insert club name]” is a not-for-profit Student Society established pursuant to Chapter 5 of the Student Guild Regulations. “[insert club name]” seeks to affiliate to the University of Western Australia Student Guild (“Guild”) Societies Council [insert “and Public Affairs Council” if applicable].
 \item This Constitution (“Constitution”) shall govern the operation of the Club and is established pursuant to Rule 144 of the Societies Council Rules.
\item Where a capitalised term is used in this Constitution but not defined, the definition shall be taken from the Societies Council Rules. Where no such definition is available the interpretation panel established under article 22.1 of this Constitution shall have the power to determine the definition of the term in question.
\item In the event of an inconsistency between this Constitution and the Societies Council Rules the provision of the Societies Council Rules shall prevail.
\end{enumerate}

\section{3. Objectives}
\begin{enumerate}[label=3.\arabic*]
\item The objective of the Club shall be to [insert club objectives].
\item An objective of the Club shall be to create a welcoming community of students which is inclusive to all, regardless of their degree, race, religion, sexual orientation or identification.
\item An objective of the Club shall be to remain affiliated to the Societies Council [insert
“and Public Affairs Council” if applicable] of the Guild.
\item An objective of the Club shall be to act in a way which promotes cooperation between the Club and other Affiliated Societies, the Societies Council, the Guild, and all of its Departments.
\item An objective of the Club shall be to do all such things necessary and proper for the benefit or advancement of Financial Members of the Club.
\item An objective of the Club shall be to apply the property and income of the Club solely to the promotion of its expressed objectives, and not, directly or indirectly, to its members, except in good faith and for the promotion of these objectives.
\item The Club must comply with this Constitution, all applicable statutes, by-laws, rules, regulations, Standing Orders, and policies in force at any given time.
\end{enumerate}

\section{4. Membership}
\begin{enumerate}[label=4.\arabic*]
    \item The Club’s membership shall be confined to Financial Members, Ordinary Committee Members, Executive Committee Members, Associate Members, and Honorary Life Members.
    \item Only Financial Members may hold voting rights at Club Elections and meetings of the Club.
    \item To be eligible to be a Financial Member a person must:
    \begin{enumerate}[label=\alph*.]
        \item Have purchased an annual membership to the Club for \$5AUD;
        \item Be a current member of the Guild; and
        \item Be an enrolled UWA student, with full rights and privileges, for the duration of their Financial Membership.
    \end{enumerate}
    \item Financial Members are entitled to:
    \begin{enumerate}[label=\alph*.]
        \item Attend and hold speaking rights at meetings of the Club;
        \item Vote on matters presented at meetings of the Club; and
        \item Stand for an Election held under the authority of and in accordance with this Constitution.
    \end{enumerate}
    \item To be an Ordinary Committee Member a person must:
    \begin{enumerate}[label=\alph*.]
        \item Be a Financial Member of the Club;
        \item Have been elected to be an Ordinary Committee Member by Financial Members in an Election held under the authority of and in accordance with this Constitution;
        \item Comply with the provisions of this Constitution and all applicable rules, regulations, and by-laws at all times; and
        \item Agree to be bound by and comply with all applicable Codes of Conduct.
    \end{enumerate}
    \item Ordinary Committee Members are, in addition to their entitlements as Financial Members, entitled to:
    \begin{enumerate}[label=\alph*.]
        \item Attend and hold speaking rights at meetings of the committee;
        \item Vote on matters presented at meetings of the committee; and
        \item Stand for election to become an Executive Committee Member.
    \end{enumerate}
    \item To be an Executive Committee Member a person must, in addition to all other requirements set out in this Constitution:
    \begin{enumerate}[label=\alph*.]
        \item Be a Financial Member of the Club;
        \item Have been elected to be an Executive Committee Member by Financial Members in an Election held under the authority of and in accordance with this Constitution;
        \item Agree to represent the Club positively in all arenas;
        \item Comply with the provisions of this Constitution and all applicable rules, regulations, and by-laws at all times; and
        \item Agree to be bound by and comply with all applicable Codes of Conduct.
    \end{enumerate}
    \item Executive Committee Members are, in addition to their entitlements as Financial Members and Ordinary Committee Members and other entitlements set out in this Constitution, entitled to:
    \begin{enumerate}[label=\alph*.]
        \item Attend and hold speaking rights at meetings of the executive committee; and
        \item Vote on matters presented at meetings of the executive committee.
    \end{enumerate}
    \item The Executive Committee shall comprise of:
    \begin{enumerate}[label=\alph*.]
        \item The President;
        \item The Vice President;
        \item The Secretary;
        \item The Treasurer; and
        \item The Immediate Past President.
    \end{enumerate}
    \item To be eligible to be an Associate Member a person must:
    \begin{enumerate}[label=\alph*.]
        \item Have purchased an annual membership to the Club for \$5AUD; and 
        \item Be or have been a Member of the Guild; or
        \item Be or have been an Associate of the Guild; or
        \item Be an Honorary Life Associate of the Guild; or
        \item Be or have been a student at the University of Western Australia.
    \end{enumerate}
    \item Associate Members are entitled to:
    \begin{enumerate}[label=\alph*.]
        \item Attend meetings of the Club.
    \end{enumerate}
    \item The Club may, in General Meeting, by two-thirds majority of those present and voting, confer Honorary Life Membership upon any member who has performed outstanding service to the Club during their tenure in office as an Ordinary Committee Member and an Executive Committee Member.
    \item Members other than Financial Members shall not:
    \begin{enumerate}[label=\alph*.]
        \item Hold speaking rights at meetings of the Club;
        \item Hold voting rights at meetings of the Club;
        \item Nominate Candidates and be nominated as a Candidate in an Election held under the authority of and in accordance with the provisions of this Constitution; or
        \item Become or remain an Executive Committee Member of the Club, or act as such.
    \end{enumerate}
    \item No University staff member may enlist or act as a member of the Club, Financial or otherwise.
\end{enumerate}

\section{5. Meeting of the Club}
\begin{enumerate}[label=5.\arabic*]
\item The Club shall hold an Annual General Meeting each year no later than the end of the second semester of the academic year as determined by the University of Western Australia from time to time.
\item The Club shall hold no less than one Ordinary General Meeting of Members per semester of the academic year.
\item The committee may at any time call a Special General Meeting of Members.
\item The Secretary shall forthwith call a Special General Meeting of Members upon receipt of a written request from no less than [insert number e.g. 15] Financial Members or no less than [insert percentage e.g. 50\%] of all Committee Members from time to time.
\item The Secretary must, within ten University Working Days of receiving such a written request, call a Special General Meeting of Members. If the Secretary fails to call such a meeting within the allotted time period any signatory to the written request may do so.
\item Any business set out in the written request shall take priority over all other business at that Special General Meeting of Members.
\end{enumerate}

\section{6. Provisions Governing General Meetings of the Club}
\begin{enumerate}[label=6.\arabic*]
\item All General Meetings of the Club (“General Meeting”), including Annual General Meetings, Ordinary General Meetings, and Special General Meetings, shall be chaired by the President.
\item Where the President is unable to chair a General Meeting the Vice President shall do so.
\item Where neither the President nor the Vice President is able to chair a General Meeting another Executive Committee Member shall do so.
\item Where no Executive Committee Member is able to chair a General Meeting an Ordinary Committee Member may nominate to do so. This nomination may be approved by simple majority of the Financial Members present and eligible to vote at the General Meeting.
\item All reports made by Executive Committee Members for the meeting must be submitted to the Secretary no less than three University Working Days prior to the meeting.
\item All motions, minutes, and supporting documentation for consideration at a General Meeting must be submitted to the Secretary no less than five University Working Days prior to the meeting, who must prepare a formal agenda therewith.
\item An agenda for the General Meeting including reports made by Executive Committee Members for the meeting and all motions, minutes, and supporting documentation submitted to the Secretary shall be distributed via all reasonable means by the Secretary no less than three University Working Days prior to the commencement of the General Meeting.
\item Subject to 6.9 a General Meeting shall only consider business of which notice has been given on the agenda, or which arises out of minutes or reports.
\item The agenda for a General Meeting may only be altered or suspended by a Procedural Motion.
\item All Financial Members, including Ordinary Committee Members and Executive Committee Members, shall be entitled to an equal vote in all motions presented to a General Meeting.
\item Any attendee of a General Meeting deemed by simple majority of Financial Members present, including Ordinary Committee Members and Executive Committee Members, to not be in their right state of mind or deemed to be disrupting the meeting may be asked to leave the General Meeting.
\item Quorum of a General Meeting shall consist of [insert percentage e.g. 20\%] of Financial Members.
\end{enumerate}

\section{7. Elections}
\begin{enumerate}[label=7.\arabic*]
\item No less than once per Guild Year the Club must hold an Election in which Ordinary
Committee Members may stand for election to become Executive Committee
members and then Financial Members may stand for election to become Ordinary
Committee Members (``Election'').

\item All club Elections shall be conducted in accordance with the Student Guild Election
Regulations and Student Guild Standing Orders.

\item All club Elections shall be conducted by optional-preferential secret ballot in
accordance with Schedule 2 of the Student Guild Election Regulations.

\item All club Elections shall be supervised by a Returning Officer.
  \begin{enumerate}[label=7.4.\arabic*]
    \item The Returning Officer shall be appointed by the Executive Committee.
    \item The Returning Officer must not have a perceived or actual conflict of interest
which could reasonably give rise to bias for or against any Candidate
standing for election.
    \item The Returning Officer must not have ever been an Ordinary Committee
Member or Executive Committee Member.
    \item The Returning Officer is responsible for ensuring the fair conduct and
administration of the Election, the electoral process of ballot creation and
counting, and winner declaration.
    \item The Returning Officer shall have the power to issue any determination in
whatever terms they see fit in order to ensure the fair conduct and
administration of the Election, and act on their own motion to prevent a
breach or attempted breach of any applicable rule or regulation
    \item Where a Returning Officer contravenes any provision of any applicable rule
or regulation, they may be dismissed by special resolution approved by a
two-thirds majority of all active committee members.
  \end{enumerate}
  
\item Nominations shall be open for no less than five University Working Days and shall
close no later than one University Working Day before the Election is to occur
(``Nomination Period'').

\item All Financial Members at the close of the Nomination Period shall be entitled to an
equal vote in each contested position in an Election.

\item To be eligible to stand for Election a person must:
  \begin{enumerate}[label=7.7.\arabic*]
    \item Be a Financial Member of the Club;
    \item Be an enrolled UWA student, with full rights and privileges, for the twelve-
month period during which they would hold office; and
    \item Agree to be bound by and comply with all applicable Codes of Conduct.
  \end{enumerate}

\item An eligible person may nominate for more than one position in the same Election,
in which case they must notify the Returning Officer of the order of their preferred
positions.

\item Nominations shall be in the form and submitted in the manner prescribed by the
Returning Officer. By submitting a nomination, the nominee agrees to be bound by
and comply with all applicable Codes of Conduct.

\item Nominations must have a proposer and a seconder to proceed. A Candidate may
propose themselves provided there is a seconder of the nomination. Both the
proposer and the seconder must be enrolled UWA students and Financial
Members of the Club.
\end{enumerate}

\section{8. Patron}
\begin{enumerate}[label=8.\arabic*]
 \item In the absence of nominations for any Ordinary or Executive Committee position, the Club’s elected executive committee may appoint a temporary patron who shall hold office until the position may be elected or appointed.
\end{enumerate}
%
\section{9. Executive Committee}
\begin{enumerate}[label=9.\arabic*]
\item The Executive Committee (``Executive Committee'') shall comprise of those positions set out in article 4.9 of this Constitution.
\item The Executive Committee shall actively govern the Club's direction during their term in office. The responsibilities of the Executive Committee include but are not limited to:
    \begin{enumerate}[label=\theenumi.\arabic*]
        \item Ensuring compliance with the Club's objectives as set out in articles 3.1 to 3.6 of this Constitution;
        \item Running at least one event per semester, in addition to an Annual General Meeting, in accordance with the Club's stated objectives and for the benefit of the Club's Financial Members;
        \item Liaising with the Societies Council Committee;
        \item Representing the Club at Societies Council General Meetings;
        \item Overseeing the Club's Ordinary Committee Members;
        \item Ensuring Executive Committee Members are compliant with training requirements set out by the Guild from time to time;
        \item Ensuring that neither the Club nor any person thereunder takes any action which represses any student's implied right to academic freedom and freedom of speech;
        \item Managing the Club's administration; and
        \item Managing the Club's finances.
    \end{enumerate}
\item No Executive Committee Member may hold more than one Executive Committee position at one time, or act as such at any time.
\item In addition to any provisions set out elsewhere in this Constitution or in any applicable by-law, rule, or regulation the President's duties shall include but shall not be limited to:
    \begin{enumerate}[label=\theenumi.\arabic*]
        \item Supervising, coordinating, delegating, and overseeing the work of the Executive Committee Members;
        \item Ensuring that each Executive Committee Member is conversant with this Constitution and their respective role;
        \item Directing the general policy of the Club;
        \item Chairing all General Meetings and meetings of the committee and the Executive Committee and reporting on the status of the Executive Committee and the Club generally at all meetings;
        \item Serving as the main point of contact between the Club and the Societies Council Committee and the Guild; and
        \item Ensuring that the Club's events and committee are inclusive environments in which members and patrons may feel safe and accepted regardless of their race, religion, sexual orientation, gender, gender presentation, and presented identity.
    \end{enumerate}
\item In addition to any provisions set out elsewhere in this Constitution or in any applicable by-law, rule, or regulation the Vice President's duties shall include but shall not be limited to:
    \begin{enumerate}[label=\theenumi.\arabic*]
        \item Supporting the President in all endeavours;
        \item Approaching, at the beginning of their term, potential sponsors and partners for the Club;
        \item Serving as the main point of contact between the Club and other Affiliated Societies; and
        \item Ensuring, in conjunction with the President, that the Club's events and committee are inclusive environments in which members and patrons may feel safe and accepted regardless of their race, religion, sexual orientation, gender, gender presentation, and presented identity.
    \end{enumerate}
    \item In addition to any provisions set out elsewhere in this Constitution or in any applicable by-law, rule, or regulation the Secretary's duties shall include but shall not be limited to:
    \begin{enumerate}[label=\theenumi.\arabic*]
        \item Preparing and keeping agendas and minutes of all club meetings;
        \item Managing administrative tasks related to the Club's operation;
        \item Supplying the Guild Finance Office with all required paperwork whenever there is a change to the Club's Executive Committee Members within twenty University Working Days of that change;
        \item Lodging any alterations made to this Constitution or any documents created under its authority with the Societies Council President for ratification within twenty University Working Days of that change;
        \item Attending Societies Council General Meetings on behalf of the Club; and
        \item Providing to the Societies Council Secretary, in the case that the Club disbands or otherwise ceases to exist, a duly audited statement of the financial position of the Club.
    \end{enumerate}
\item In addition to any provisions set out elsewhere in this Constitution or in any applicable by-law, rule, or regulation the Treasurer's duties shall include but shall not be limited to:
    \begin{enumerate}[label=\theenumi.\arabic*]
        \item Directing the Club's financial affairs;
        \item Ensuring that all events hosted by the Club are financially viable;
        \item Keeping records of all of the Club's incomes and expenditures throughout their term;
        \item Paying all invoices charged to the Club in a timely manner;
        \item Preparing a thorough budget for every event hosted by the Club;
        \item Preparing and submitting all required forms and receipts such that the Club may receive grants from the Societies Council Committee;
        \item Declaring to Guild Finance and the Societies Council Committee any donation or in-kind support received from sources other than grants provided to the Club by the Guild, regardless of the source or amount; and
        \item Ensuring that grants provided to the Club are used only for the purposes of providing services or amenities to the Club's membership, that all expenditure of funds received via grants complies with conditions attached to that grant, and that the Club complies with all applicable financial regulations.
    \end{enumerate}
\item Executive Committee Members' term in office shall begin immediately following their election and shall end at the next Club Election.
\item Executive Committee Members may be impeached where the member in question has committed any act or omission which constitutes Guild misconduct, or where a vote of no confidence is approved in accordance with the procedures set out in articles 9.9.1 to 9.9.3 of this Constitution.
    \begin{enumerate}[label=\theenumi.\arabic*]
        \item Where a vote of no confidence is approved by unanimous vote of the Executive Committee Members (excluding the member whose impeachment is being considered) the member in question shall be impeached.
        \item No less than [insert percentage e.g. two thirds] Financial Members may call a Special General Meeting with the intent to impeach an Executive Committee Member. The member in question must be granted the opportunity to present a case for their own defence. Where a vote of no confidence is approved by no less than [insert percentage e.g. two thirds] Ordinary Committee Members the member in question shall be impeached.
    \end{enumerate}
\end{enumerate}

\section{10. Casual Vacancies}
\begin{enumerate}[label=10.\arabic*]
 \item Where an Executive Committee Member resigns, is impeached, or ceases to hold office during their expected term for any other reason, the casual vacancy shall be filled by an Ordinary Committee Member being appointed by the remaining Executive Committee until the vacant position may be filled at an Election. 
\end{enumerate}
%
\section{11. Ordinary Committee}
\begin{enumerate}[label=11.\arabic*]
\item Included in the Club's Ordinary Committee Membership at all times except before the first committee intake of the calendar year, there shall be no less than [insert number] ``First Year Representatives,'' [insert ``at least 50\% of which are female or gender diverse'' where number is above 1].
 \item To be eligible to be elected as a ``First Year Representative'' a person must be in the first year of their university degree.
\end{enumerate}

\section{12. Non-Discrimination}
\begin{enumerate}[label=12.\arabic*]
 \item The Club and its committee always act in a manner which gives no special treatment, favour, advantage or disadvantage to any group of people, and shall vigorously defend the right of all members to feel safe and accepted within the community.
\end{enumerate}

\section{13. Expulsion from Committee}
\begin{enumerate}[label=13.\arabic*]
\item Any Financial, Ordinary, or Executive Committee Member who, in the unanimous opinion of the Executive Committee, or a two-thirds majority opinion of the ordinary committee, contravenes article 12.1 to such an extent that the Club or another individual is directly and detrimentally harmed, may immediately have their membership revoked.
\item Any Financial, Ordinary, or Executive Committee Member who is found to be encouraging or enforcing disciplinary measures for non-participation in any sort of initiation ceremony or encourages or requires participation in any sort of initiation ceremony as a precondition of membership to the committee may immediately have their membership revoked.
\item Any Financial, Ordinary, or Executive Committee Member who is found to be taking or have taken any action which represses any student's implied right to academic freedom and freedom of speech may immediately have their membership revoked.
\item Any member, Financial, Ordinary, Executive, or Associate, only have their membership suspended or removed in accordance with articles 13.1 to 13.3 of this Constitution, or in the following circumstances:
    \begin{enumerate}[label=\theenumi.\arabic*]
        \item They are no longer eligible to be a member under the provisions of this Constitution; or
        \item They are subject to suspension, expulsion, or other disciplinary action by the University.
    \end{enumerate}
\end{enumerate}

\section{14. Power and Responsibilities of the Committee}
\begin{enumerate}[label=14.\arabic*]
\item Subject to other articles of this Constitution, the committee shall be responsible for:
    \begin{enumerate}[label=14.1.\arabic*]
    \item Pursuing the Club's objectives set out in article 3 of this Constitution;
    \item Carrying out the day-to-day business of the Club; and
    \end{enumerate}

\item Without prejudice to the generality of the foregoing, the committee shall, in cases where the committee has approved by simple majority a motion providing such authority, have the power to:
    \begin{enumerate}[label=14.2.\arabic*]
    \item Acquire and dispose of property;
    \item Deposit and receive sums of money;
    \item Open bank accounts;
    \item Enter into contracts;
    \item Make, alter, and repeal regulations for the orderly and proper management of the Club's affairs, to the extent that no provision of such regulations is repugnant with this constitution; and
    \item Make, alter, and repeal by-laws specifying any part of this constitution, to the extent that no provision of such by-laws is repugnant with this constitution.
    \end{enumerate}

\item Unless acting under a special enabling resolution of a general meeting, the committee shall not incur debts or liabilities on behalf of or in the name of the Club.

\item The Executive Committee may hold records of the Club's members, including private information as it relates to the individual's membership of the Club.
    \begin{enumerate}[label=14.4.\arabic*]
    \item Records must be used only for purposes relating to the Club and its activities. The Club and its Executive Committee must protect the security and privacy of members' personal information which it holds records of.
    \end{enumerate}

\item The committee shall be responsible for reporting suspected Guild Misconduct in relation to the Club's Financial, Ordinary Committee, Executive Committee, Associate, or Honorary Life Members to the appropriate Guild, University, or Government authorities. The committee shall not have the power to take disciplinary action against a member of its own accord past revoking that person's membership.
\end{enumerate}

\section{15. Deposits and Withdrawals of Monies}
\begin{enumerate}[label=15.\arabic*]
 \item All monies due and payable to the Club must be received by the Treasurer. In cases where the Treasurer is unable to receive the payment the President may do so on their behalf.
\item All withdrawals from the Club's bank accounts must be authorised by the Treasurer.
\item All payments from the Club's bank accounts must be authorised and processed by the Treasurer in a timely manner.
\end{enumerate}
%
\section{16. Payments}
\begin{enumerate}[label=16.\arabic*]
 \item No payment shall be made on behalf of or in the name of the Club unless it has been authorised by the Treasurer or approved by simple majority by the committee.
\end{enumerate}

\section{17. Major Obligations to the Guild}
\begin{enumerate}[label=17.\arabic*]
 \item The Club shall at all times comply with all regulations and directions of the Guild and the Societies Council Committee, including but not limited to compliance with mandatory training as required by the Guild or Societies Council Committee including but not limited to Guild Student Leadership Training.
\item All Executive and Ordinary Committee Members shall be jointly and severally responsible for such compliance and shall be deemed liable in the event of noncompliance therewith.
\item An Executive Committee Member must be present at every Societies Council General Meeting hosted by the Guild.
\end{enumerate}

\section{18. Dispute Resolution}
\begin{enumerate}[label=18.\arabic*]
\item Where a dispute arises, the parties to the dispute must attempt to resolve the dispute between themselves within ten University Working Days of the dispute coming to the attention of each party.
\item If the parties to a dispute are unable to resolve the dispute between themselves within the time period set out in article 18.1 of this Constitution, any party to the dispute may start the dispute resolution process set out herein by providing written notice of the dispute to the parties to the dispute and to the following, who shall act as Mediator ("Mediator") in relation to the dispute:
    \begin{enumerate}[label=18.2.\arabic*]
    \item Where the dispute is between the Club and another Affiliated Society, the Governance Committee;
    \item Where the dispute is with the Societies Council, the Societies Council President, or if they are unable to act, another Executive Member of the Societies Council Committee;
    \item Where the dispute is between a Financial Member and the Club, the Executive Committee Members;
    \item Where the dispute is between Financial Members of the Club, the Executive Committee Members;
    \item Where the dispute is between Financial Members of the Club in respect of a Financial Member's expulsion from Financial Membership, the Governance Committee.
    \end{enumerate}
\item The Mediator to a dispute must act in compliance with the articles 72 to 80 of the Societies Council Rules.
\end{enumerate}

\section{19. Transparency of documentation}
\begin{enumerate}[label=19.\arabic*]
\item The Secretary must, upon request, provide the minutes of any committee meeting and all records of the committee's decisions and policy to any Financial, Ordinary Committee, or Executive Committee Member who makes such a request.
\item The Treasurer must, upon request, provide financial records of any decision, policy, or payment to any Financial, Ordinary Committee, or Executive Committee member who makes such a request.
\item The Executive Committee must, upon request, provide any record or documentation requested to any member of the Societies Council Committee Executive or Guild Executive who makes such a request.
\end{enumerate}


\section{20. Availability of this constitution}
\begin{enumerate}[label=20.\arabic*]
 \item The committee shall make this Constitution freely available upon request to any Financial Member or Guild Member at any time.
\end{enumerate}

\section{21. Alteration of this constitution}
\begin{enumerate}[label=21.\arabic*]
\item Any alteration proposed to be made to this Constitution must be submitted in writing to the Secretary no less than five University Working Days before the General Meeting in which the alteration is to be proposed.
\item Any Financial Member of the Club, with a seconder (also being a Financial Member), may propose an alteration to this Constitution. Both the proposer and seconder must be present at the General Meeting at which the alteration is to be discussed.
\item Any alteration made to this Constitution must be authorised by two-thirds of the Financial Members present and eligible to vote at the General Meeting at which the alteration is to be discussed.
\item Any alteration made to this Constitution shall come into effect upon ratification by the Societies Council President.
\item This Constitution replaces all previous rules governing the administration of the Club.
\end{enumerate}

\section{22. Interpretation of this constitution}
\begin{enumerate}[label=22.\arabic*]
\item In the event of a contest regarding the interpretation of any part of this Constitution the contest shall be reviewed by a panel consisting of the President, Vice President, and three Ordinary Committee Members selected by the committee.
    \begin{enumerate}[label=22.1.\arabic*]
    \item In the event that a decision of the panel is contested, a Financial Member may raise the contested part at a General Meeting, at which time the interpretation of the disputed part will be decided by simple majority.
    \end{enumerate}
\end{enumerate}

\section{23. Dissolution of the Club}
\begin{enumerate}[label=23.\arabic*]
 \item In the case that the Club dissolves, disbands, or otherwise ceases to exist, if any property of the Club remains after the satisfaction of any debts or liabilities that the Club may have, that property shall be transferred into liquid assets by the Club’s final Treasurer and transferred to the Societies Council Committee.
\end{enumerate}

\section{24. Adoption}
\begin{enumerate}[label=24.\arabic*]
     \item This Constitution has been adopted by the Club at its General Meeting on
    \begin{enumerate}[label=24.1.\arabic*]
     \item \hspace{1cm} \makebox[3cm]{\hrulefill} (date)
    \end{enumerate}
   \item This Constitution has been ratified by the Societies Council President being
    \begin{enumerate}[label=24.2.\arabic*]
     \item \hspace{1cm} \makebox[3cm]{\hrulefill} (signed) on 
     \item \hspace{1cm} \makebox[3cm]{\hrulefill} (date)
    \end{enumerate}
\end{enumerate}
\end{document}
